Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-24 man/figures/growth_changes.Rmd
line size

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .3, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.3) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black') +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

@@

```{r plot_SJ}
psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) + 
  xlab('') + 
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1)+
  annotate("text", x = 1990, y = 440, label = "SJ", fontface = 2, size = 3)

>>>>

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .2, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.2) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black', lwd=0.2) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

@@

```{r plot_SJ}
psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) + 
  xlab('') + 
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1,  lwd=0.2)+
  annotate("text", x = 1990, y = 440, label = "SJ", fontface = 2, size = 3)
